---
title: "HW3"
author: "Will"
date: "7 de junio de 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)





```


## HW3

###Question 1

A situation in my work where I might use exponential smoothing could be inflation forecast. We use CPI as a input for expected rate of return. Monthly CPI tend to looks seasonally with respect to its history. So I could use a algoritm to determinate the best smoothing parameter, choises the lower square error. If that not the case I think that I could use 0.5. 



###Question 2

```{r echo = T, eval = T, warning=FALSE, message=TRUE}

library(forecast)


setwd("C:/Users/ce02144/Documents/HW3")
#Reading data
weather <- read.table("temps2.txt", header = TRUE)

#Converting to timeserie
weather.ts <- ts(weather[,2:21], 
                 frequency = 123)

#Create model
model = HoltWinters(x = weather.ts, beta = FALSE, seasonal = "multiplicative")

#Exploring results
model

plot(fitted(model), plot.conf=FALSE, type="o", fcol="white", xlab="Time")

```

The level in fitted results shows that end of summer has been gotten later in recent years. However, taking into account the 20year history that trend is not very clear.  


###Question 3

A linear regression problem for could be *Colombian Currency Forecast*	


**As a predictors I could use:**  
CPI actual  
CPI Forecast  	
Central Bank Rate	actual  
Central Bank Forecast	
GDP actual  
Consumer Sentiment  
US vs Colombian bonds yield spread
Price of insurance cost for colombian goverment debt



###Question 4

```{r echo = T, eval = T, warning=FALSE, message=TRUE}


library(ggplot2)
library(MASS)
library(leaps)
library(relaimpo)

setwd("C:/Users/ce02144/Documents/HW3")

#Reading data
uscrime <- read.table("uscrime.txt", header = TRUE)

#Creating model
model = lm(Crime~., data = uscrime) 

#Analyzing model
summary(model)
coefficients(model)
AIC(model)
BIC(model)

#Calculing the relative importance of predictors
# Bootstrap Measures of Relative Importance (5 samples) 
boot <- boot.relimp(model, b = 5, type = c("lmg"), rela = TRUE)
plot(booteval.relimp(boot,sort = TRUE), las = 2, cex.axis = 0.5, srt = 60, adj = 1) 


#Prediction test
M = 14.0
So = 0
Ed = 10.0
Po1 = 12.0
Po2 = 15.5
LF = 0.640
M.F = 94.0
Pop = 150
NW = 1.1
U1 = 0.120
U2 = 3.6
Wealth = 3200
Ineq = 20.1
Prob = 0.04
Time = 39.0

question4 <- data.frame(M, 
                        So, 
                        Ed, 
                        Po1, 
                        Po2, 
                        LF, 
                        M.F,
                        Pop,
                        NW,
                        U1,
                        U2,
                        Wealth,
                        Ineq,
                        Prob,
                        Time
                        )

#crime prediction
predict(model, newdata = question4,type = "response" )

#we could look for better model using leaps library
#nbest best model for each combination.

leaps <- regsubsets(Crime~., data = uscrime, nbest = 1)

# Plot alternative models by bic. There are same predictors but different intercepts

plot(leaps, scale = "bic")

# Plot alternative models by bic. There are same predictors but different intercepts
plot(leaps, scale = "r2")



```





